Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-10-29 Report/mse_formulation.tex
second update without W

In all simulations, the objective of Algorithm \ref{algo-1} converges. \reviewF{However, to discuss the theoretical convergence of subproblems \eqref{eqn-9}, \eqref{eqn-9--1} and \eqref{eqn-mse-2}, following modifications are considered. (i) Instead of \eqref{eqn-6.1} and \eqref{eqn-mse-2.1}, we consider a regularized objective with quadratic term as in \eqref{mod_obj} to ensure strong convexity in objective function. (ii) To guarantee the boundedness of feasible sets, we trivially bound \eqn{\beta_{l,k,n}}'s and \eqn{\mvec{w}{l,k,n}}'s as \eqn{\beta_{l,k,n} \leq P_{\max}} and \eqn{\|\mvec{w}{l,k,n}\|^2 \leq 1} in subproblems \eqref{eqn-9} and \eqref{eqn-9--1}. However, these additional constraints on optimization variables has no impact on final solution or objective. Using this, convergence of Algorithm \ref{algo-1} is discussed in Appendix \ref{sec-3.5}.}

>>>>

In all simulations, the objective of Algorithm \ref{algo-1} converges. \reviewF{However, to discuss the theoretical convergence of subproblems \eqref{eqn-9}, \eqref{eqn-9--1} and \eqref{eqn-mse-2}, following modifications are considered. (i) Instead of \eqref{eqn-6.1} and \eqref{eqn-mse-2.1}, we consider a regularized objective with quadratic term as in \eqref{mod_obj} to ensure strong convexity in objective function. (ii) To guarantee the boundedness of feasible sets in \eqref{eqn-9} and \eqref{eqn-9--1}, we include an additional constraint on  \eqn{\beta_{l,k,n}} as \eqn{\beta_{l,k,n} \leq P_{\max}} without affecting the solution. It restricts \eqn{\beta_{l,k,n}} from taking \eqn{\infty} when \eqn{\gamma_{l,k,n} = 0} for inactive users, since \eqref{eqn-6.3} need not be active. Using these, convergence of Algorithm \ref{algo-1} is discussed in Appendix \ref{sec-3.5}.}
